Compositional equivalences based on Open pNets

### 2020-09-08 2016-Weak-FH-Bisim/Coverletter.tex

>>>>

Finally, after a brief exchange with Alexandra Silva, we improved the form of the paper as follows. We improved the spacings here and there (e.g. between subscripts and rest of text) and tracked overfull boxes. We also adopted a reduced number of symbols and tried to reduce the use of $<....>$ to the synchronisation vectors where this notation is usual now.
